Kung Faux Pandas \\ \large Simplifying privacy protection

### 2018-06-05 paper/short_version.tex
Auto Update from local Sharelatex

Recent work has clarified the definition and importance of reproducibility and a closely related concept, replicability. Leek and Peng have defined reproducibility as the "ability to recompute data analytic results given an observed dataset and knowledge of the data analysis pipeline," and replicability as "the chance that an independent experiment targeting the same scientific question will produce a consistent result."\cite{leek_opinion_2015,peng_reproducible_2006} Others have used the terms in a reverse fashion\cite{drummond_replicability_2009}. Despite the semantic differences, there is broad agreement that an independent experiment with confirmatory results is the strongest support of any experiment. One early influential paper on the topic of reproducibility in scientific computing lists the key factors in reproducibility as available data, input parameters, documentation, software code, and an environment capable of running the provided software code. These items are difficult to completely convey in a traditional research paper \cite{schwab_making_2000}.

@@

Many domains in which ML investigators work have legal barriers that make it difficult to enable independent verification of ML models which frequently require enormous amounts of training data. As an example, in the health care domain in the United States, a key law governing health data is the Health Insurance Portability and Accountability Act (HIPAA). HIPAA is backed by significant civil penalties as well as specifics about data security and what can and cannot be done with protected health information \cite{hippaviol}. While there are other domain specific data privacy laws, there are also some broad rules that affect entire countries such as the European Union's General Data Protection Regulation (GDPR). The GDPR puts in place new rules about data ownership and control in an attempt to give individuals more control over their information.

The current legal environment creates a difficult situation for scientists in the health care domain. Early examples of re-identification attacks \cite{sweeney_2002} have have created apprehension on the part of businesses and legal experts in data sharing \cite{ohm_broken_2009}. Getting access to source health care data is slow and isn't always granted \cite{hodge_legal_1999, committee_hipaa_privacy_rule_2009}. More recently, research in the data sharing/privacy protection space has focused more on synthesis techniques such as in the case of the Synthea system \cite{walonoski_synthea_2018}. Current solutions are not without their drawbacks however as they frequently require significant configuration of metadata before they can generate data or they attempt to solve the entire solution space and consequently are very slow to run.

@@

KFP addresses the issue of data access by generating data that is ``statistically similar'' to the real data but does not itself contain any sensitive data. We collectively refer to de-identified data and synthetic data as \emph{faux-data}. We use the term faux as it is used in the fashion sense of the word: the use of man made materials that look and feel like real leather, fur, etc., but without the problematic derivation from live animals and reliance upon limited resources. This faux-data can be analyzed, cleaned, feature-engineered, etc. as if it were the actual source data. KFP provides a standard mechanism for wrapping a privacy protection method into a plug-in which integrates the method with the Pandas DataFrame model. Two of these plug-ins are provided with full documentation for creating other plug-ins.

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=120mm]{data_synthesis_process}
  \caption{Data synthesis process.}
  \label{fig:synthesis_process}
\end{figure}

Figure~\ref{fig:synthesis_process} shows the automated faux-data request/response process. All queries submitted to the system are first pre-processed to remove clauses such as "ORDER BY" which are made ineffective by the synthesis process. All queries are logged for later analysis and results cached to optionally improve synthesis performance for repeated queries. Next the processed query is executed against the protected data set and results are passed into the modular synthesis process. While the current implementation only utilizes a couple of synthesis methods, ML developers or data warehouse owners can insert their own custom method or modify existing methods. Previously removed "ORDER BY" clauses are re-applied to the faux-data before results are returned to the user. Finally, although not implemented in this version of KFP, synthetic results could be held back until reviewed and approved for release by the data owner.

\begin{wrapfigure}[16]{r}{0.5\textwidth}%optionally place [15] after {wrapfigure} to control how many lines to wrap around figure
  \centering
  \includegraphics[width=0.5\textwidth]{ui_screenshot3}
  \caption{User Interface.}
  \label{fig:ui}
\end{wrapfigure}

@@

KFP provides a unique contribution to the space of reproducible ML. Through providing ad-hoc faux-data, ML researchers can have lower barriers to accessing private data as well as reduced barriers to sharing faux-data derived from private data. However, there are several areas that could be improved or researched further: improved code sharing, addressing institutional specific privacy issues, and evaluation of this system in a ML workflow.

While we have provided software code and a description of our methods, we believe that ML reproducibility should go beyond just making source code available. Peng recommends making code available in any form as an excellent first step towards reproducible research; the next step is to make code available "in a durable non-proprietary format" \cite{peng_reproducible_2011}. This is a level of code sharing rarely achieved in ML research. Currently there is no standard long term format that works for all computational environments. For the Python ecosystem however, the standard for sharing code is via a package on Python Package Index (PyPI). We intend to continue this research to make KFP available as a Python package.

Another area that is open for further research is that of domain and institution specific data privacy needs. In the field of education, statistical methods for calculating sample size based on probability of detecting a specific effect size are commonly used \cite{naep_2009} as the key method for privacy protection. However, it is not clear that these methods are appropriate for use in ML in general or domains other than education. Thus, in this work, no attempt has been made to constrain data set sizes nor provide additional proofs of data protection. KFP could be modified to return no results if a minimum threshold is not met or, alternatively, data boosting techniques in combination with data synthesis could be used based on the risk profile of the data owner(s).

The last area recommended for further research is to deploy and observe the use of KFP in an active ML environment where researchers are working with sensitive datasets. A key limitation that may be identified is that of performance characteristics, particularly in a multi-user setting against a large relational database store. Additionally, as no private data was distributed via this system, actual review by security and compliance groups or institutional review boards may uncover additional requirements to reduce risk of data exposure that could require significant rework or further study.

>>>>

Recent work has clarified the definition and importance of reproducibility and a closely related concept, replicability. Leek and Peng have defined reproducibility as the "ability to recompute data analytic results given an observed dataset and knowledge of the data analysis pipeline," and replicability as "the chance that an independent experiment targeting the same scientific question will produce a consistent result."\cite{leek_opinion_2015,peng_reproducible_2006} There is broad agreement that an independent experiment with confirmatory results is the strongest support of any experiment. One early influential paper on the topic of reproducibility in scientific computing lists the key factors in reproducibility as available data, input parameters, documentation, software code, and an environment capable of running the provided software code. These items are difficult to convey in a traditional research paper \cite{schwab_making_2000}.

@@

Many domains in which ML investigators work have legal barriers that make it difficult to enable independent verification of ML models due to data access issues. As an example, in the health care domain in the US, a key law governing health data is the Health Insurance Portability and Accountability Act (HIPAA). HIPAA is backed by significant civil penalties, specifics about data security, and what can be done with protected health information \cite{hippaviol}. While there are other domain specific data privacy laws, there are also some broad rules such as the European Union's General Data Protection Regulation (GDPR). The GDPR puts in place new rules about data ownership and control in an attempt to give individuals more control over their information.

Early examples of re-identification attacks \cite{sweeney_2002} have have created apprehension on the part of businesses and legal experts in data sharing \cite{ohm_broken_2009}. More recently, research in the data sharing/privacy protection space has focused more on synthesis techniques such as in the case of the Synthea system \cite{walonoski_synthea_2018}. Current solutions are not without their drawbacks however as many require significant configuration of metadata before they can generate data or they attempt to solve the entire solution space and consequently are very slow to run.

@@

KFP addresses the issue of data access by generating data that is similar to the real data but does not itself contain any sensitive data. We collectively refer to de-identified data and synthetic data as \emph{faux-data}. We use the term faux as it is used in the fashion sense of the word: the use of man made materials that look and feel like real leather, fur, etc., but without the problematic derivation from live animals and reliance upon limited resources. Faux-data can be analyzed, cleaned, modeled etc. as if it were the actual source data. KFP provides a standard mechanism for wrapping a privacy protection method into a plug-in which integrates the method with the Pandas DataFrame model. Two of these plug-ins are provided with full documentation for creating other plug-ins.

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=120mm]{prototype_architecture}
  \caption{System Architecture.}
  \label{fig:architecture}
\end{figure}\begin{figure}[ht]
  \centering
  \includegraphics[width=100mm]{data_synthesis_process}
  \caption{Data synthesis process.}
  \label{fig:synthesis_process}
\end{figure}

Figure~\ref{fig:synthesis_process} shows the automated faux-data request/response process. All queries submitted to the system are first pre-processed to remove clauses such as "ORDER BY" which are made ineffective by the synthesis process. All queries are logged for later analysis and results cached to optionally improve synthesis performance for repeated queries. Next the processed query is executed against the protected data set and results are passed into the modular synthesis process. While the current
\begin{wrapfigure}[15]{r}{0.5\textwidth}%optionally place [15] after {wrapfigure} to control how many lines to wrap around figure
  \centering
  \includegraphics[width=0.5\textwidth]{ui_screenshot3}
  \caption{User Interface.}
  \label{fig:ui}
\end{wrapfigure}
implementation only utilizes a couple of synthesis methods, ML developers or data owners can insert their own custom method or modify existing methods. Previously removed "ORDER BY" clauses are re-applied to the faux-data before results are returned to the user. Finally, although not implemented in this version of KFP, synthetic results could be held back until reviewed and approved for release by the data owner.

@@

KFP provides a unique contribution to the space of reproducible ML. Through providing ad-hoc faux-data, ML researchers can have lower barriers to accessing private data as well as reduced barriers to sharing faux-data derived from private data. However, there are several areas that could be researched further: improved code sharing, addressing institutional specific privacy issues, and evaluation of this system in a ML workflow.

While we have provided software code and a description of our methods, we believe that ML reproducibility should go beyond just making source code available. Peng recommends that code should be made available "in a durable non-proprietary format" \cite{peng_reproducible_2011}. This is a level of code sharing rarely achieved in ML research. Currently there is no standard long term format that works for all computational environments. For the Python ecosystem however, the standard for sharing code is via a package on Python Package Index (PyPI). We intend to continue this research to make KFP available as a Python package.

Another area that is open for further research is that of domain and institution specific data privacy needs. In the field of education, statistical methods for calculating sample size based on probability of detecting a specific effect size are commonly used \cite{naep_2009} as the key method for privacy protection. However, it is not clear that these methods are appropriate for use in ML in general or domains other than education. KFP could be modified to return no results if a minimum threshold is not met or, alternatively, data boosting techniques in combination with data synthesis could be used based on the risk profile of the data owner(s).

The last area recommended for further research is to deploy and observe the use of KFP in an active ML environment where researchers are working with sensitive datasets. A key limitation that may be identified is that of performance characteristics, particularly in a multi-user setting against a large relational database store. Additionally, actual reviews by security and compliance groups or institutional review boards may uncover additional requirements to reduce risk of data exposure that could require significant rework or further study.
